Carbonate chemistry at Ny-Ålesund

### 2022-08-02 awipev-CO2.Rmd
still messing with gtsummary

range_month <-
  d_all %>%
  dplyr::select(sal_fb_mix) %>% 
#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
    #group_by(montht) %>%
#tbl_summary(by = montht, missing = "no",
tbl_summary(missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",    # line 1: mean and SD
              "{median}",
             # "{p25}, {p75})",  # line 2: median and IQR
              "{min}",
              "{max}")
) #%>% 
  #add_n() %>% 
  #modify_header(label = "**Variable**") %>%
  #bold_labels()# %>% 
  #as_gt()
range_month

>>>>

range_month <-
  d_all %>%
  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
    #group_by(montht) %>%
tbl_summary(by = montht,
            missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",
              "{median}",
              "{p25}",
              "{p75}",
              "{min}",
              "{max}"),
            digits = list(all_continuous() ~ c(2, 1, 1, 3)))
range_month
tbl_summary(missing = "no",
            type = sal_fb_mix ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",    # line 1: mean and SD
              "{median}",
              "{p25}", 
              "{p75}",  # line 2: median and IQR
              "{min}",
              "{max}")
) #%>% 
  #add_n() %>% 
  #modify_header(label = "**Variable**") %>%
  #bold_labels()# %>% 
  #as_gt()
range_month
